\Title

### 2021-04-01 latex/paper/main.tex
Edit of acrobot and experiment section

%/========== Acrobot ==========/%
\section{The Acrobot VNHC}\label{sec:acrobot}
%specialize the theory of VNHCs to the acrobot. consider constraints which depend
%only on pu, and show arctan vnhc and reduced dynamics. 
%give definition of energy injection/dissipation. conclude with our
%theorem. Make this section short and sweet.
%
%TODO: after writing S2, re-introduce what we want to do with acrobot (energy
%injection for giant stabilization)
Our goal in this article isto design a VNHC which injects energy into the
acrobot through giant-like motion.
We use the simplified acrobot model acrobot in Figure
\ref{fig:simple-acrobot-model}, where we assume the torso and leg rods
are of equal length \(l\) with equal point masses \(m\) at the tips.
A real gymnast cannot swing their legs in full circles, though they
are usually flexible enough to raise them parallel to the floor;
hence, we assume the leg angle \(q_a\) lies in \([-Q_a, Q_a]\) for some
\(Q_a \in [\frac{\pi}{2}, \pi[\). 
We also ignore any frictional forces.

@@

The acrobot has inertia matrix 
\(M\), potential function \(V\) (with respect to
the horizontal bar), and input matrix \(B\) given as follows:
\begin{align}\label{eqn:acrobot-inertia}
    M(q) &= \begin{bmatrix}
        ml^2\left(3+2\cos(q_a)\right) & 
        ml^2\left(1+\cos(q_a)\right) \\
        ml^2\left(1+\cos(q_a)\right) &
        ml^2
    \end{bmatrix} 
    , \\
    \label{eqn:acrobot-potential}
    V(q) &= -mgl\left(2\cos(q_u)+\cos(q_u+q_a)\right)
    , \\
    \label{eqn:acrobot-B}
    B &= [0;1]
    .
\end{align}
The conjugate of momenta is \(p = (p_u,p_a) = M(q)\dot{q}\).
The dynamics of the acrobot in \((q,p)\) coordinates are given in
~\eqref{eqn:acrobot-hamiltonian}, where
for shorthand, we write \(c_u := \cos(q_u)\), \(c_a := \cos(q_a)\), and 
\(c_{ua} := \cos(q_u + q_a)\); likewise, \(s_u := \sin(q_u)\), 
\(s_a := \sin(q_a)\), and \(s_{ua} := \sin(q_u + q_a)\).
\begin{align}\label{eqn:acrobot-hamiltonian}
    \mathcal{H}(q,p) &= \frac{1}{2}p\tpose \Minv(q) p -
    mgl\left(2 c_u + c_{ua}\right)
    , \\
     &\begin{cases}
        \dot{q} = \Minv(q) p 
        ,\\
        \dot{p}_u = -mgl\left(2s_u + s_{ua}\right) 
        ,\\
        \dot{p}_a =-\frac{1}{2}p\tpose \nabla_{q_a}\Minv(q) p
        - mgl s_{ua} + \tau,
    \end{cases} \nonumber
\end{align}
The control input is a force \(\tau \in \R\) affecting only the dynamics of
\(p_a\), representing a torque acting on the hip joint.
This means \((q,p)\) are simply actuated coordinates inside the phase space
\(\mathcal{Q} \times \mathcal{P}\) where
\(\mathcal{Q} = \Sone \times \Sone\), and
\(\mathcal{P} = \R \times \R\).
We can therefore apply the theory of VNHCs from Section \ref{sec:vnhc} to design
a constraint of the form \(q_a = f(q_u,p_u)\). 
This constraint must inject energy into the acrobot according to
Definition \ref{defn:energy-injection}.
Since we need the VNHC to be regular, the following proposition will prove
useful.
\begin{prop}\label{prop:acrobot-fpu-regular}
    A relation \(h(q,p) = q_a - f(p_u) = 0\) 
    with \(f \in C^2\left(\R; \Sone\right)\) is a regular
    VNHC of order 1 for the simple acrobot.
\end{prop}
\begin{proof}
    The regularity matrix for this VNHC evaluates to
    \(\frac{(1+c_a)\partial_{q_u}f(q_u,p_u) + (3+2c_a)}{ml^2(2-c_a^2)}\).
    Since \(\partial_{q_u} f = 0\), this matrix is strictly positive for all values
    of \(q_a\), and hence is full rank everywhere on the constraint manifold.
\end{proof}

To design our VNHC, we begin by examining a person on a
seated swing.
The person extends their legs when the swing moves forwards, and retracts their
legs when the swing moves backwards.
As the swing gains speed, the person leans their body back while
extending their legs higher, thereby shortening the distance
from their center of mass to the pivot and adding more energy to the swing
\cite{how_to_pump_a_swing}.

@@

Recall that \((q_u, p_u)\) denote the angle and momentum of the acrobot's torso.
By Theorem \ref{thm:zero-dynamics}, we can study the constrained system by
examining solely the motion of \((q_u,p_u) \in \SxR\).
It is easy to show that the constrained dynamics are
\begin{equation}\label{eqn:acrobot-constrained-dynamics}
    \begin{cases}
    \dot{q}_u &= \frac{(1+I^2 p_u^2)p_u + m^2gl^3\bar{q}_a I(2s_u + s_{ua})(1+c_a) }
            {ml^2(1+I^2 p_u^2)(3+2c_a)}
    ,    \\
    \dot{p}_u &= - m g l (2s_u + s_{ua})
    ,
    \end{cases}
\end{equation}
subject to \(q_a = \bar{q}_a \arctan(I p_u)\).
These are just the torso dynamics when one swings the legs
according to \eqref{eqn:acrobot-constraint}.

@@

Unfortunately, our VNHC does not always inject energy on \(\mathcal{O}_1\) and
\(\mathcal{O}_2(\bar{\rho})\).
If \(I\) is too large, the leg controller saturates (i.e. the legs swing up too
quickly) and the body may not swing higher. 
However, choosing \(I\) small enough guarantees the legs will synchronize
properly with the body, and the acrobot will begin doing backflips on the bar.
The following theorem provides conditions under which such an \(I\) exists.

\begin{thm}\label{thm:acrobot-energy-stabilization}
    Consider the acrobot with Hamiltonian dynamics, as in ~\eqref{eqn:acrobot-hamiltonian}.
\begin{enumerate}
    \item For any \(m\), \(g\), \(l\), \(\bar{q}_a\), there exists
        \(I^\star > 0\) such that, for all \(I \in \, ]0,I^\star]\), the VNHC
        ~\eqref{eqn:acrobot-constraint} injects energy into the acrobot on
        \(\mathcal{O}_1\).
        Moreover, almost every orbit will escape the closure of
        \(\mathcal{O}_1\) in finite time.
        If instead \(I \in [-I^\star,0[\), the VNHC dissipates energy.
    \item Let \(C = m^2gl^3\bar{q}_a\) and 
        define \(b : \SxR_{> 0} \rightarrow \R\) by
    \[
        b(\beta,\rho_0) := 
        \frac{5C \left(
        \frac{C}{\bar{q}_a}\left(18s_\beta^2 + 30c_\beta(1 - c_\beta)\right)
            - c_\beta\rho_0^2
        \right)}{
        |\rho_0|\sqrt{\rho_0^2 - 30m^2gl^3(1 - c_\beta)}
        }
        .
    \]
        Define 
        \(S(\rho_0) := \int \limits_{0}^{2\pi} b(\sigma,\rho_0)d\sigma\).
        Fix \(\bar{\rho} > \sqrt{60m^2gl^3}\) and
        suppose there exists \(\epsilon > 0\) so that 
        \(S(\rho_0) \geq \epsilon\) for all 
        \(\rho_0 \in \, \left]\sqrt{60m^2gl^3}, \bar{\rho}\right]\).
        Then there exists \(I^{\star\star} \in \, ]0, I^\star]\) such that, for all 
        \(I \in \, ]0,I^{\star\star}]\), the VNHC
        ~\eqref{eqn:acrobot-constraint} injects energy into the acrobot on
        \(\mathcal{O}_2(\bar{\rho})\).
        If instead \(I \in [-I^{\star\star},0[\), the VNHC dissipates energy.
\end{enumerate}
\end{thm}
\begin{proof}
    See Section \ref{sec:proof}.
\end{proof}

@@

For the acrobot to achieve giants with energy
\(E(0,\bar{\rho})\), it must satisfy the assumption on the integral
of \(b(\beta,\rho_0)\). 
The value of this integral depends on the acrobot's physical parameters.
If the assumption holds, there is some control value \(I > 0\)
(which depends on \(\bar{\rho}\)) for which the acrobot will 
achieve rotations with a momentum of at least \(\bar{\rho}\).

%/========== Experiments ==========/%
\section{Experimental Results}\label{sec:experiments}
In this section, we test our VNHC on the physical acrobot built by
Xingbo Wang \cite{xingbo_thesis} (Figure \ref{fig:xingbo-acrobot}).
The torso and leg rods on this robot have unequal mass and differ in length, so
its inertia matrix and potential function are not described correctly by 
~\eqref{eqn:acrobot-inertia}-\eqref{eqn:acrobot-potential}.
These experiments will therefore show that VNHCs are robust to model mismatch.

@@

The control parameter \(I\) must be small to satisfy Theorem
\ref{thm:acrobot-energy-stabilization}, but it must also be large enough to
overcome friction in the servo motor.
We experimentally determined that \(I = 10\) is sufficient to
ensure the actuator can fully rotate in its allowable range
\(q_a \in \left[ -\frac{\pi}{2}, \frac{\pi}{2}\right]\).

\subsection{Simulations Results}
Evaluating the true mechanical energy of Wang's acrobot at the VNHC
\(q_a = 0\) yields the energy of the nominal pendulum,
\[
    E(q_u,p_u) \approx 396.5501 p_u^2 + 0.5997(1 - \cos(q_u))
    .
\]
We simulated Wang's acrobot starting at 
\((q_u,p_u) = \left(\frac{\pi}{32},0 \right)\) and plotted the resulting orbit
in Figure \ref{fig:acrobot-orbit}.

The set \(E_\pi := E(\pi,0)\) is outlined in black. 
Because of model mismatch, \(E_\pi\) is no longer the boundary between
rotations and oscillations.
The oscillation domain is actually much larger: orbits rotate once they hit the
\(p_u\)-axis at \(\abs{p_u} \approx 0.15\), while \(E_\pi\) intersects the
\(p_u\)-axis at \(\abs{p_u} \approx 0.055\).
Despite this, the VNHC still injects energy into the acrobot.
The points where the orbit exits \(E_\pi\) are marked with black stars,
with the final departure marked with a red star.
After this final departure, the acrobot begins rotating and continues to gain
energy over time.

\begin{figure}[h]
    \centering
    \begin{subfigure}[t]{0.45\linewidth}
        \includegraphics[width=\linewidth]{acrobot_orbit.png}
        \caption{Orbit initialized at \((q_u,p_u) = (\pi/32,0)\).}
        \label{fig:acrobot-orbit}
    \end{subfigure}
    \begin{subfigure}[t]{0.45\linewidth}
        \includegraphics[width=\linewidth]{acrobot_mc.png}
        \caption{Monte Carlo results.}
        \label{fig:acrobot-mc}
    \end{subfigure}
    \caption{Simulations using Wang's acrobot \cite{xingbo_thesis}.}
\end{figure}

To verify that the acrobot would always achieve rotations, we ran a
Monte-Carlo simulation \cite{montecarlo}:
we initialized the acrobot randomly inside the sublevel set
\[
    \left\{(q_u,p_u) \in \SxR \mid
    E(q_u,p_u) \leq E\left(\frac{\pi}{32},0\right)\right\}
    ,
\] 
and measured the how long it took to begin rotating.
The results in Figure \ref{fig:acrobot-mc} show that
the acrobot always rotated within 10--35 seconds.

\subsection{Physical Experiments}
Wang's acrobot has an encoder at the pivot which measures \(q_u\) and
\(\dot{q}_u\).
The leg actuator is a servo motor with a built-in PID controller, which provides
measurements of \(q_a\).
We estimate \(\dot{q}_a\) through sequential values of \(q_a\) and
compute \(p_u\) through \(p_u = e_1^T M(q) \dot{q}\).
We then assign the actuator value at iteration \(k \in \mathbb{Z}_{> 0}\)
via \(q_a^{k} = \arctan(I p_u^{k-1})\).

\textbf{Baseline Test:} 
for this test, we initialized the acrobot at 
\((q_u,p_u) \approx \left(\frac{\pi}{8},0\right)\). 
The resulting orbit is shown in Figure \ref{fig:acrobot-unperturbed-orbit};
the acrobot is clearly gaining energy over time.

@@

\textbf{Stop Test:}
for this test we initialized the acrobot at 
\((q_u,p_u) \approx \left(\pi,0\right)\), let it run for 15
seconds, then stopped it at the bottom of its arc.
The resulting orbit is shown in Figure \ref{fig:acrobot-stopped-orbit}.
The blue curves correspond to the orbit before the disturbance, while the red
spiral confirms that the acrobot begins oscillating after it is stopped.
Despite the disturbance, it gains energy and eventually starts rotating
again.

\textbf{Push Test:}
to see how the acrobot responds when pushed, we allowed
the acrobot to rotate undisturbed for 15 seconds and then pushed it in its
direction of motion.
The orbit in Figure \ref{fig:acrobot-fpush-orbit} shows that the acrobot speeds
up to rotate with energy \(E(0,0.22)\), but then slows down until it reaches a
stable rotation with energy \(E(0,-0.195)\).
We repeated this test by pushing the acrobot against its direction of motion.
The orbit in Figure \ref{fig:acrobot-rpush-orbit} demonstrates that the acrobot
responds by readily changing direction, and quickly achieves its maximum speed
with energy \(E(0,0.195)\).

These push tests suggest that our VNHC injects energy into Wang's acrobot on
\(\mathcal{O}_2(0.195)\).

@@

\subsection{Summary of Experiments}
These simulations and experiments demonstrate that VNHCs are excellent
tools for injecting energy, even with significant model mismatch.
In particular, energy injection through VNHCs appears to be robust against a
variety of disturbances.

>>>>

%/========== Acrobot ==========/%
\section{The Acrobot VNHC}\label{sec:acrobot}
%specialize the theory of VNHCs to the acrobot. consider constraints which depend
%only on pu, and show arctan vnhc and reduced dynamics. 
%give definition of energy injection/dissipation. conclude with our
%theorem. Make this section short and sweet.
%
%TODO: after writing S2, re-introduce what we want to do with acrobot (energy
%injection for giant stabilization)
Our goal in this article is to design a VNHC which injects energy into the
acrobot through giant-like motion.
We will use the simplified acrobot model in Figure
\ref{fig:simple-acrobot-model}, where we assume the torso and leg rods are of
equal length \(l\) with equal point masses \(m\) at the tips.
A real gymnast cannot swing their legs in full circles, though they
are usually flexible enough to raise them parallel to the floor;
hence, we assume the leg angle \(q_a\) lies in \([-Q_a, Q_a]\) for some
\(Q_a \in [\frac{\pi}{2}, \pi[\). 
We also ignore any frictional forces.

@@

The acrobot has inertia matrix 
\(M\), potential function \(V\) (with respect to
the horizontal bar), and input matrix \(B\) given as follows:
\begin{align}\label{eqn:acrobot-inertia}
    M(q) &= \begin{bmatrix}
        ml^2\left(3+2\cos(q_a)\right) & 
        ml^2\left(1+\cos(q_a)\right) \\
        ml^2\left(1+\cos(q_a)\right) &
        ml^2
    \end{bmatrix} 
    , \\
    \label{eqn:acrobot-potential}
    V(q) &= -mgl\left(2\cos(q_u)+\cos(q_u+q_a)\right)
    , \\
    \label{eqn:acrobot-B}
    B &= [0;1]
    .
\end{align}
The conjugate of momenta is \(p = (p_u,p_a) = M(q)\dot{q}\).
The dynamics of the acrobot in \((q,p)\) coordinates are given in
~\eqref{eqn:acrobot-hamiltonian}, where
for shorthand, we write \(c_u := \cos(q_u)\), \(c_a := \cos(q_a)\), and 
\(c_{ua} := \cos(q_u + q_a)\); likewise, \(s_u := \sin(q_u)\), 
\(s_a := \sin(q_a)\), and \(s_{ua} := \sin(q_u + q_a)\).
\begin{align}\label{eqn:acrobot-hamiltonian}
    \mathcal{H}(q,p) &= \frac{1}{2}p\tpose \Minv(q) p -
    mgl\left(2 c_u + c_{ua}\right)
    , \\
     &\begin{cases}
        \dot{q} = \Minv(q) p 
        ,\\
        \dot{p}_u = -mgl\left(2s_u + s_{ua}\right) 
        ,\\
        \dot{p}_a =-\frac{1}{2}p\tpose \nabla_{q_a}\Minv(q) p
        - mgl s_{ua} + \tau,
    \end{cases} \nonumber
\end{align}
The control input is a force \(\tau \in \R\) affecting only the dynamics of
\(p_a\), representing a torque acting on the hip joint.
This means \((q,p)\) are simply actuated coordinates in the phase space
\(\mathcal{Q} \times \mathcal{P}\) where
\(\mathcal{Q} = \Sone \times \Sone\), and
\(\mathcal{P} = \R \times \R\).
We can therefore apply the theory from Section \ref{sec:vnhc} to design
a VNHC of the form \(q_a = f(q_u,p_u)\). 
Since we need the VNHC to be regular, the following proposition will prove
useful.
\begin{prop}\label{prop:acrobot-fpu-regular}
    A relation \(h(q,p) = q_a - f(p_u) = 0\) 
    with \(f \in C^2\left(\R; \Sone\right)\) is a regular
    VNHC of order 1 for the acrobot.
\end{prop}
\begin{proof}
    The regularity matrix for the acrobot evaluates to
    \(((1+c_a)\partial_{q_u}f(q_u,p_u) + (3+2c_a))/(ml^2(2-c_a^2))\).
    Since \(\partial_{q_u} f = 0\), this matrix is strictly positive for all values
    of \(q_a\), and hence is full rank everywhere on the constraint manifold.
\end{proof}

To design our VNHC, we begin by examining a person on a
seated swing.
The person extends their legs when the swing moves forwards, and retracts their
legs when the swing moves backwards.
As the swing gains speed, the person leans their body while
extending their legs higher, thereby shortening the distance
from their center of mass to the pivot and adding more energy to the swing
\cite{how_to_pump_a_swing}.

@@

Recall that \((q_u, p_u)\) denote the angle and momentum of the acrobot's torso.
By Theorem \ref{thm:zero-dynamics}, the constrained acrobot is parameterized
fully by \((q_u,p_u) \in \SxR\).
It is easy to show that the constrained dynamics are
just the torso dynamics obtained when one swings the legs
according to \eqref{eqn:acrobot-constraint}; that is, they are
\begin{equation}\label{eqn:acrobot-constrained-dynamics}
    \begin{cases}
    \dot{q}_u &= \frac{(1+I^2 p_u^2)p_u + m^2gl^3\bar{q}_a I(2s_u + s_{ua})(1+c_a) }
            {ml^2(1+I^2 p_u^2)(3+2c_a)}
    ,    \\
    \dot{p}_u &= - m g l (2s_u + s_{ua})
    ,
    \end{cases}
\end{equation}
subject to \(q_a = \bar{q}_a \arctan(I p_u)\).

@@

Unfortunately, our VNHC does not always inject energy on \(\mathcal{O}_1\) and
\(\mathcal{O}_2(\bar{\rho})\).
If \(I\) is too large, the leg controller saturates and the body oscillates
without gaining energy.
Choosing \(I\) small enough guarantees the legs will synchronize
properly with the body, and the acrobot will begin rotating around the bar.
The following theorem provides conditions under which such an \(I\) exists.

\begin{thm}\label{thm:acrobot-energy-stabilization}
    Consider the acrobot with Hamiltonian dynamics as in ~\eqref{eqn:acrobot-hamiltonian}.
\begin{enumerate}
    \item For any \(m\), \(g\), \(l\), \(\bar{q}_a\), there exists
        \(I^\star > 0\) such that, for all \(I \in \, ]0,I^\star]\), the VNHC
        ~\eqref{eqn:acrobot-constraint} injects energy into the acrobot on
        \(\mathcal{O}_1\).
        Moreover, almost every orbit will escape the closure of
        \(\mathcal{O}_1\) in finite time.
        If instead \(I \in [-I^\star,0[\), the VNHC dissipates energy.
    \item Let \(C = m^2gl^3\bar{q}_a\) and 
        define \(b : \SxR_{> 0} \rightarrow \R\) by
    \[
        b(\beta,\rho_0) := 
        \frac{5C \left(
        \frac{C}{\bar{q}_a}\left(18s_\beta^2 + 30c_\beta(1 - c_\beta)\right)
            - c_\beta\rho_0^2
        \right)}{
        |\rho_0|\sqrt{\rho_0^2 - 30m^2gl^3(1 - c_\beta)}
        }
        .
    \]
        Define 
        \(S(\rho_0) := \int \limits_{0}^{2\pi} b(\sigma,\rho_0)d\sigma\).
        Fix \(\bar{\rho} > \sqrt{60m^2gl^3}\) and
        suppose there exists \(\epsilon > 0\) so that 
        \(S(\rho_0) \geq \epsilon\) for all 
        \(\rho_0 \in \, \left]\sqrt{60m^2gl^3}, \bar{\rho}\right]\).
        Then there exists \(I^{\star\star} \in \, ]0, I^\star]\) such that, for all 
        \(I \in \, ]0,I^{\star\star}]\), the VNHC
        ~\eqref{eqn:acrobot-constraint} injects energy into the acrobot on
        \(\mathcal{O}_2(\bar{\rho})\).
        If instead \(I \in [-I^{\star\star},0[\), the VNHC dissipates energy.
\end{enumerate}
\end{thm}
\begin{proof}
    See Section \ref{sec:proof}.
\end{proof}

@@

For the acrobot to achieve giants with energy
\(E(0,\bar{\rho})\), it must satisfy the assumption on the integral
of \(b(\beta,\rho_0)\). 
The value of this integral depends on the acrobot's physical parameters.
If the assumption holds, there is some control value
(which depends on \(\bar{\rho}\)) for which the acrobot will 
achieve rotations with a momentum of at least \(\bar{\rho}\).

%/========== Experiments ==========/%
\section{Experimental Results}\label{sec:experiments}
We tested our VNHC on the physical acrobot built by
Xingbo Wang \cite{xingbo_thesis} (Figure \ref{fig:xingbo-acrobot}).
The torso and legs on this robot have differing masses and lengths, so
its inertia matrix and potential function are \textbf{not} described by 
~\eqref{eqn:acrobot-inertia}-\eqref{eqn:acrobot-potential}.
If our VNHC injects energy into this acrobot, then we can infer that
VNHCs are robust to model mismatch.

@@

For our VNHC to inject energy, we know the control parameter \(I\) must be small
(as per Theorem \ref{thm:acrobot-energy-stabilization}), but it must also be
large enough to overcome friction in leg motor.
Setting \(\bar{q}_a = 1\), we experimentally determined that \(I = 10\) is
sufficient to ensure the actuator can fully rotate in its allowable range \(q_a
\in \left[ -\frac{\pi}{2}, \frac{\pi}{2}\right]\). 
Rhis is the value of \(I\) we used in all simulations and experiments.

\subsection{Simulations Results}
Evaluating the true mechanical energy of Wang's acrobot at the VNHC
\(q_a = 0\) yields the energy of the nominal pendulum,
\[
    E(q_u,p_u) \approx 396.5501 p_u^2 + 0.5997(1 - \cos(q_u))
    .
\]
We simulated Wang's acrobot with initial condition
\((q_u,p_u) = \left(\pi/32,0 \right)\) and plotted the resulting orbit
in Figure \ref{fig:acrobot-orbit}.

The set \(E_\pi := E(\pi,0)\) is outlined in black. 
Due to the model mismatch, \(E_\pi\) is no longer the boundary between
rotations and oscillations.
The oscillation domain is actually much larger: orbits rotate once they hit the
\(p_u\)-axis at \(\abs{p_u} \approx 0.15\), while \(E_\pi\) intersects the
\(p_u\)-axis at \(\abs{p_u} \approx 0.055\).
Despite this, the VNHC still injects energy into the acrobot.
The points where the orbit exits \(E_\pi\) are marked with black stars,
with the final departure marked with a red star.
After this final departure, the acrobot begins rotating and continues to gain
energy over time.

\begin{figure}[]
    \centering
    \includegraphics[width=0.7\linewidth]{acrobot_orbit.png}
    \caption{A simulated orbit of Wang's acrobot.}
    \label{fig:acrobot-orbit}
\end{figure}
To verify numerically that the acrobot would consistently achieve rotations, we
ran a Monte-Carlo simulation \cite{montecarlo} where we initialized the acrobot
randomly inside the sublevel set
\[
    \left\{(q_u,p_u) \in \SxR \mid
    E(q_u,p_u) \leq E\left(\frac{\pi}{32},0\right)\right\}
    ,
\] 
and measured the how long it took to begin rotating.
The results in Figure \ref{fig:acrobot-mc} show that
the acrobot always rotated within 10--35 seconds.

\begin{figure}[]
    \centering
    \includegraphics[width=0.7\linewidth]{acrobot_mc.png}
    \caption{Monte Carlo simulation results.}
    \label{fig:acrobot-mc}
\end{figure}

\subsection{Physical Experiments}

Wang's acrobot has an encoder which measures \(q_u\) and
\(\dot{q}_u\).
Additionally, the leg actuator is a servo motor with a built-in PID controller
which provides measurements of \(q_a\).
To implement our VNHC, we estimated \(\dot{q}_a\) through sequential values of
\(q_a\) and computed \(p_u\) through \(p_u = e_1^T M(q) \dot{q}\).
We directly assigned the actuator setpoint at iteration \(k \in \mathbb{Z}_{> 0}\)
via \(q_a^{k} = \arctan(10 p_u^{k-1})\).
We then performed the following tests.

\begin{enumerate}
    \item \textbf{Baseline Test:} 
    we initialized the acrobot at 
    \((q_u,p_u) \approx \left(\frac{\pi}{8},0\right)\). 
    The resulting orbit is shown in Figure \ref{fig:acrobot-unperturbed-orbit};
    the acrobot is clearly gaining energy over time.

@@

\item \textbf{Stop Test:}
    we initialized the acrobot at 
    \((q_u,p_u) \approx \left(\pi,0\right)\), let it run for 15
    seconds, then stopped it at the bottom of its arc.
    The resulting orbit is shown in Figure \ref{fig:acrobot-stopped-orbit}.
    The blue curves correspond to the orbit before the disturbance, while the red
    spiral confirms that the acrobot begins oscillating after it is stopped.
    Despite the disturbance, it gains energy and eventually starts rotating
    again.

\item \textbf{Push Test:}
    to see how the acrobot responds when pushed, we allowed
    the acrobot to rotate undisturbed for 15 seconds and then pushed it in its
    direction of motion.
    The orbit in Figure \ref{fig:acrobot-fpush-orbit} shows that the acrobot speeds
    up to rotate with energy \(E(0,0.22)\), but then slows down until it reaches a
    rotation with energy \(E(0,-0.195)\).
    We repeated this test by pushing the acrobot against its direction of motion.
    The orbit in Figure \ref{fig:acrobot-rpush-orbit} demonstrates that the acrobot
    responds by readily changing direction, and quickly achieves its maximum speed
    with energy \(E(0,0.195)\).

    These push tests suggest that our VNHC injects energy into Wang's acrobot on
    \(\mathcal{O}_2(0.195)\).
\end{enumerate}

@@

\subsection{Summary of Results} 
These simulations and experiments demonstrate that VNHCs are excellent
tools for injecting energy.
In particular, energy injection through VNHCs appears to be robust against a
variety of disturbances, including significant model mismatch.
